### 2018-05-04 dissertation.tex
appdx 3; uamk models

\hypersetup{pdftitle={Essays in Political and Criminal Violence},
	pdfauthor={Danilo Alves M. Freire},
	pdfborder={0 0 0},
	breaklinks=true,
	linkcolor=black,
	citecolor=Mahogany,
	urlcolor=darkblue,
	colorlinks=true}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In the third essay, co-authored with Gary Uzonyi, we employ extreme bounds analysis and distributed random forests to identify the key determinants of state-sponsored violence. We test the sensitivity of 40 variables on a sample of 177 countries from 1945 to 2013. The results show that GDP per capita, democracy, and the post-Cold War period are negatively associated with mass killings, whereas ethnic diversity, civil wars, and previous political turmoils increase the risk of state-led violence. GDP per capita, years since the last episode of mass violence, urban population, ethnic polarisation, and the number of military personnel make the greatest contribution to the models' out-of-sample predictive power.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% ACKNOWLEDGEMENTS HERE:
I would like to extend thanks to the many people, in many countries, who so generously contributed to the work presented in this thesis. First and foremost, I want to thank my supervisor, Professor David Skarbek. It was a great privilege and honour to work and study under his guidance, and he has taught me more than I could ever give him credit for here. David was not only an excellent supervisor but also a great friend; his empathy, enthusiasm, and sense of humour made my stay at King's College a very pleasant one. I simply could not have wished for a better mentor for my PhD studies. Thank you very much.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TABLE OF CONTENTS, LISTS OF TABLES & FIGURES
\newpage
\pdfbookmark[0]{Contents}{contents_bookmark}
\tableofcontents
\listoftables
\phantomsection
\addcontentsline{toc}{chapter}{List of Tables}
\listoffigures
\phantomsection
\addcontentsline{toc}{chapter}{List of Figures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\hypersetup{pdftitle={Essays in Political and Criminal Violence},
	pdfauthor={Danilo Alves M. Freire},
	pdfborder={0 0 0},
	breaklinks=true,
	linkcolor=Mahogany,
	citecolor=Mahogany,
	urlcolor=darkblue,
	colorlinks=true}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In the third essay, I employ extreme bounds analysis and distributed random forests to identify the key determinants of state-sponsored violence. Although the literature on mass killings has grown significantly over the last decades, it remains unclear whether estimates are robust to different model specifications or which variables accurately predict the onset of genocides and politicides. To address this issue, I test the sensitivity of 40 variables on a sample of 177 countries from 1945 to 2013. The results show that GDP per capita, the post-Cold War period, and stable political regimes are negatively associated with mass killings. In contrast, ethnic diversity, civil wars, and previous political turmoils increase the risk of state-led violence. Mass killings that occur during civil wars are correlated with a different set of variables, and I find that territorial conflicts and the use of militias are negatively associated with the outcome. The random forests estimations indicate that years since the last episode of mass violence, GDP per capita, urban population, ethnic polarisation, the number of military personnel, and democracy make the greatest contribution to the models' out-of-sample predictive power.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% ACKNOWLEDGEMENTS HERE:
I would like to extend thanks to the many people, in many countries, who so generously contributed to the work presented in this thesis. First and foremost, I want to thank my supervisor, Professor David Skarbek, for the guidance and encouragement he provided me. David was not only an excellent supervisor but also a great friend; his empathy, enthusiasm, and sense of humour made my stay at King's College a very pleasant one. I could not have wished for a better mentor for my PhD studies. Thank you very much.

@@

I am heartily grateful to my examiners, Professor Toke Aidt and Professor Graham Denyer Willis, who accepted to dedicate their precious time to evaluate this work.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TABLE OF CONTENTS, LISTS OF TABLES & FIGURES
\newpage
{\hypersetup{linkcolor=black}
\pdfbookmark[0]{Contents}{contents_bookmark}
\tableofcontents
\listoftables
\phantomsection
\addcontentsline{toc}{chapter}{List of Tables}
\listoffigures
\phantomsection
\addcontentsline{toc}{chapter}{List of Figures}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
